Networked Character Devices

### 2011-12-11 report/paper.tex
paper: I meant 'for'

Most importantly, \texttt{struct cdev} ties together the major/minor
number with the given set of file operations. With this it is possible
for a kernel module to register many major/minor numbers (typically
a contiguous range), while having fine-grained control over which
subsets are handled by which distinct groups of file operations. This
will be important in the future as specific subsystems are handled
differently by NCD to increase functionality.

>>>>

Most importantly, \texttt{struct cdev} ties together the major/minor
number with the given set of file operations. With this it is possible
for a kernel module to register for many major/minor numbers (typically
a contiguous range), while having fine-grained control over which
subsets are handled by which distinct groups of file operations. This
will be important in the future as specific subsystems are handled
differently by NCD to increase functionality.
